%-------------------------
% Resume in Latex
% Author : Shania Brown
% Based off of: Jakes Resume - https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Shania Brown} \\ \vspace{1pt}
    \small 513-289-6944 $|$ \href{mailto:x@x.com}{\underline{Shaniabrown203@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{https://www.linkedin.com/in/shania-brown-9b368023b}} $|$
    \href{https://github.com/...}{\underline{https://github.com/ShaniaB417}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Seidenberg School of CSIS, Pace University}{New York, NY}
      {Masters of Science in Computer Science}{Expected Graduation: May 2026}
    \resumeSubheading
      {School of Engineering Technology, Farmingdale State College }{Farmingdale, NY}
      {Bachelor of Science, Major in Computer Programming and Information Systems }{Aug. 2020 -- May 2024}
  \resumeSubHeadingListEnd



  %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, SQL , JavaScript, HTML, CSS } \\
     \textbf{Frameworks}{: Bootstrap, React, ThreeJS, Vite } \\
     \textbf{Software and Tools}{:Blender, Unity, Microsoft SQL Server, Git } \\
     \textbf{Methodologies}{: Agile Development, DevOps Deployment}
    }}
 \end{itemize}


%-------------------------------------------


%-----------EXPERIENCE-----------
\section{Leadership and Events}
  \resumeSubHeadingListStart

    \resumeSubheading
      {NASA Space Apps Challenge Hackathon Team Leader}{October 2023}
      {GitHub Repository: \href{https://github.com/ShaniaB417/Star-Travel-Tourism}{Star Travel Tourism}}{Syosset, NY}
      \resumeItemListStart
        \resumeItem{Led a diverse team in the NASA Space Apps Challenge Hackathon, facilitating collaborative efforts to tackle a complex problem in space technology and exploration.}
        \resumeItem{Created a tool that developed customized itineraries for future travelers who want to visit the planets of our solar system and educate present-day users about our solar system through innovative problem-solving.}
        \resumeItem{Effectively managed and motivated team members, assigning tasks, ensuring deadlines were met, and fostering a creative and productive work environment}
      \resumeItemListEnd
    
    \resumeSubheading
      {NYCWiC Conference Participant}{April 2024}
      {GitHub Repository: \href{https://github.com/ShaniaB417/Day-At-The-Park}{Day At The Park}}{New York, NY}
      \resumeItemListStart
        \resumeItem{Led the development of "Day At The Park," an immersive virtual reality game where players act as park rangers.}
        \resumeItem{Oversaw the implementation of Unity and Blender to create an engaging experience, rewarding players for completing tasks and unlocking features.}
        \resumeItem{Implemented a DevOps deployment methodology to streamline project management processes.}
        \resumeItem{Ensured efficient collaboration among team members.}
        \resumeItem{Maintained version control using Unity Version Control.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
    
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Sole Swap} $|$ \emph{ReactJS, Vite, HTML/CSS, Firebase}}{October 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Sneaker trading website facilitating exchanges without purchases.}
            \resumeItem{Followed intuitive UI/UX design for seamless user experience for implementation for front end.}
            \resumeItem{Implemented Firebase for secure backend, including account creation and login.}
            \resumeItem{Followed Agile Development methodologies for project management.}
            \resumeItem{GitHub Repository: \href{https://github.com/ShaniaB417/Sole-Swap}{Sole Swap}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{EnergySaver} $|$ \emph{PHP, HTML/CSS, JavaScript}}{May 2023 -- April 2024}
          \resumeItemListStart
            \resumeItem{Developed an Energy portal that users can login and upload their reports and calculate their energy usage using PHP, SQL, and JavaScript.}
            \resumeItem{Designed and developed an intuitive user interface with HTML/CSS, creating a seamless experience for users to navigate through the portal.}
            \resumeItem{GitHub Repository: \href{https://github.com/ShaniaB417/EnergySaver}{EnergySaver}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \item{\textbf{VR Developer Pathway  } - Unity Learn (In Progress)}
    \item{\textbf{AR Developer Pathway } - Unity Learn (In Progress)}
  \resumeSubHeadingListEnd


%

\end{document}
